Baseline centering problem

### 2018-12-10 paper/tangotd.tex

Eligibility traces are a random, unbiased estimator of $G$: if
$(s_t)_{t\in \Z}$ is a
trajectory from the current policy then
\begin{equation}
\E\sum_{k\geq 1}\partial_\psi \log \pi(a_{t-k}|s_{t-k})\1_{s_t}=G
\end{equation}
Moreover $G$ satisfies a backward Bellman equation on-policy,
\begin{equation}
G=\E_{s,a,s'} \partial_\psi \log \pi(a|s)\1_{s'}+GP
\end{equation}
thanks to $\Delta^{-1}=\sum P^k=\Id+\Delta^{-1}P$. Eligibility traces are
precisely
updated this way at each step, via a sampling of $P$.

$G$ cannot be stored but one can store an approximate model. For instance
one could approximate $G$ as a sum of parameters times functions:
\begin{equation}
G\approx \sum_i \psi_i \phi_{\theta_i}(s)
\end{equation}
where each $\psi_i$ is a policy parameter, and each $\phi_{\theta_i}$ is
a function of the state parameterized by some model. Then the reverse
Bellman equation above allows us to learn $\psi_i$ and $\theta_i$ via 
a TD-like algorithm, \emph{on-policy}.

>>>>

Eligibility traces are a random, unbiased estimator of $G$: if
$(s_t)_{t\in \Z}$ is a
trajectory from the current policy then
\begin{equation}
\E\sum_{k\geq 1}\partial_\psi \log \pi(a_{t-k}|s_{t-k})\1_{s_t}=G
\end{equation}
namely, if $v$ is the eligibility trace vector, then the expectation of
$\transp{v}\1_{s_t}$ is $G$, at every time $t$.

Moreover $G$ satisfies a backward Bellman equation on-policy,
\begin{equation}
G=\E_{s,a,s'} \partial_\psi \log \pi(a|s)\1_{s'}+GP
\end{equation}
thanks to $\Delta^{-1}=\sum P^k=\Id+\Delta^{-1}P$. Eligibility traces are
precisely
updated this way at each step, via a sampling of $P$.

$G$ cannot be stored but one can store an approximate model. For instance
one could approximate $G$ via a neural network with input $s$ and output
in the policy parameter space. \footnote{The policy parameter space may
be quite large. This means the neural network should have a small
next-to-last layer. Indeed, with a next-to-last layer of size $r$,
the weights of the last layer are represented by $r$ policy parameters.
This corresponds to a rank-$r$ approximation of $G$,
as a sum of parameters times functions:
\begin{equation}
G\approx \sum_i \psi_i \phi_i(s)
\end{equation}
where each $\psi_i$ is a policy parameter, and each $\phi_i$ is
a function of the state, corresponding to a feature in the network.} Then the reverse
Bellman equation above allows us to learn this model via
a TD-like algorithm, \emph{on-policy}.
